### 2017-02-24 IROS17/intro.tex
Updated the paper part
All the codes and pictures added(some pictures to be added)

\section{Introduction}\label{sec:Intro}
Particle swarms propelled by a global field are common in applied mathematics, biology, and computer graphics. 
%If the $i$th particle has position $[x_i,y_i]$ and velocity $[\dot{x}_i, \dot{y}_i]$, then
%\begin{align}
%[\dot{x}_i, \dot{y}_i]^\top = \mathbf{u}(t), \qquad i \in [1,n]. \label{eq:swarmDynamics} %[u_x, u_y]^\top
%\end{align}
%These system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\citep{Purcell1977}. 
% In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the robots.  
%  The same model can be generalized to particles moved by fluid flow where the vector direction of fluid flow $\mathbf{u}(t)$ controls the velocity of particles, or for a swarm of robots that move at a constant speed in a direction specified by a global input $\mathbf{u}(t)$~\citep{Rubenstein2012}.
% Our control problem is to design the control inputs $\mathbf{u}(t)$ to make all $n$ particles achieve a task.
As a current example, micro- and nano-robots can be manufactured in large numbers, see~\citep{Chowdhury2015,martel2014computer,kim2015imparting,Donald2013,Ghosh2009,Ou2013,qiu2015magnetic}.
Someday large swarms of robots will be remotely guided
to assemble structures in parallel and 
 through the human body to cure disease, heal tissue, and prevent infection. %Both tasks are high   as described in \citep{munoz2014review} \citep{sitti2015biomedical} . 
 For each task, large numbers of micro robots are required to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
They require techniques to shape the swarm that can reliably exploit large populations despite severe underactuation ($2 \ll2n$).

@@

\begin{figure}
\centering
\begin{overpic}[width=0.95\columnwidth]{IntroSwarmPic.pdf}\end{overpic}
\caption{\label{fig:IntroPic}
Swarm of kilobots programmed to move toward the brightest light source as explained in Sec.  \ref{sec:expResults}. The current covariance ellipse and mean are shown in red, the desired covariance is shown in green.  Navigating a swarm using global inputs is challenging because each member receives the same control inputs. 
This paper focuses on using boundary walls and wall friction to break the symmetry caused by the global input and control the shape of a swarm. See multimedia attachment for overview of the experiments.} \vspace{-1em}
\end{figure}

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\citep{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
%Even without obstacles or boundaries, the mean position of the swarm in \eqref{eq:swarmDynamics} is controllable.  By adding rectangular boundary walls, some higher-order moments, such as the swarm's position variance orthogonal to the boundary walls ($\sigma_x$ and $\sigma_y$ for a workspace with axis-aligned walls), are also controllable~\citep{ShahrokhiIROS2015}. 
%A limitation is that global control can only compress a swarm orthogonal to obstacles, but navigating through narrow passages often requires control of the variance and the covariance of the swarm.
%These techniques could only compress a swarm orthogonal to obstacles.
Swarm shape control is necessary for navigation through narrow passages, for self-assembly, and for manipulating objects.

>>>>

\section{Introduction}\label{sec:Intro}
Particle swarms propelled by a global field are common in applied mathematics, biology, and computer graphics. 
%If the $i$th particle has position $[x_i,y_i]$ and velocity $[\dot{x}_i, \dot{y}_i]$, then
%\begin{align}
%[\dot{x}_i, \dot{y}_i]^\top = \mathbf{u}(t), \qquad i \in [1,n]. \label{eq:swarmDynamics} %[u_x, u_y]^\top
%\end{align}
%These system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\citep{Purcell1977}. 
% In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the robots.  
%  The same model can be generalized to particles moved by fluid flow where the vector direction of fluid flow $\mathbf{u}(t)$ controls the velocity of particles, or for a swarm of robots that move at a constant speed in a direction specified by a global input $\mathbf{u}(t)$~\citep{Rubenstein2012}.
% Our control problem is to design the control inputs $\mathbf{u}(t)$ to make all $n$ particles achieve a task.
As a current example, micro- and nano-robots can be manufactured in large numbers, see~\citep{Chowdhury2015}-\citep{qiu2015magnetic}.
Someday large swarms of robots will be remotely guided
to assemble structures in parallel and 
 through the human body to cure disease, heal tissue, and prevent infection. %Both tasks are high   as described in \citep{munoz2014review} \citep{sitti2015biomedical} . 
 For each task, large numbers of micro robots are required to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
They require techniques to shape the swarm that can reliably exploit large populations despite severe underactuation ($2 \ll2n$).

@@

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\citep{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
%Even without obstacles or boundaries, the mean position of the swarm in \eqref{eq:swarmDynamics} is controllable.  By adding rectangular boundary walls, some higher-order moments, such as the swarm's position variance orthogonal to the boundary walls ($\sigma_x$ and $\sigma_y$ for a workspace with axis-aligned walls), are also controllable~\citep{ShahrokhiIROS2015}. 
%A limitation is that global control can only compress a swarm orthogonal to obstacles, but navigating through narrow passages often requires control of the variance and the covariance of the swarm.
%These techniques could only compress a swarm orthogonal to obstacles.
Swarm shape control is necessary for navigation through narrow passages, for self-assembly, and for manipulating objects.
\begin{figure}
\centering
\vspace{1.5em}
\begin{overpic}[width=0.47\columnwidth]{story3Moves1.pdf}\put(40, 102){n=2}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{story3Moves4.pdf}\put(10, 102){Optimal shortest path}\end{overpic}\\
\vspace{1em}
\begin{overpic}[width=0.43\columnwidth]{monalizaBegin.pdf}\put(30, 100){n=862}\put(16,60){goal}\put(30,20){robots}\end{overpic}
\begin{overpic}[width=0.38\columnwidth]{monalisa.pdf}\put(-3, 102){position control algorithm}\put(7,25){final configuration}\end{overpic}
\caption{\label{fig:IntroPic}
Dynamic algorithm to find the shortest path for two robots is designed. The two top pictures shows the initial position and goal position of the robots and the optimal shortest path by making use of wall friction when shared control input is applied. The two bottom pictures shows the n robot positioning using shared control input and boundary walls. 
} \vspace{-1em}
\end{figure}

### 2017-02-24 IROS17/theory.tex
All the codes and pictures added(some pictures to be added)

\subsection{Using Boundaries: Friction and Boundary Layers}\label{subsec:WallFriction}
Global inputs move a swarm uniformly.  
Shape control requires breaking this uniform symmetry.  
A swarm inside an axis-aligned rectangular workspace can reduce variance normal to a wall by simply pushing the swarm into the boundary. 
If the swarm can flow around each other, pushing the swarm into a boundary produces the limited set of configurations presented in Sec.~\ref{subsec:FluidInTank}.
%Controlling covariance by pushing the swarm into a boundary requires changes to the boundary.  
%An obstacle in the lower-right corner is enough to generate positive covariance, but generating both positive and negative covariance requires additional obstacles.  
%Requiring a special obstacle configuration also makes shape control dependent on the local environment. 
Instead of pushing our robots directly into a wall, the following sections examine an oblique approach  using boundaries that generate friction with the robots. 
 These frictional forces are  sufficient to break the symmetry caused by uniform inputs.  
Robots touching a wall have a friction force that opposes movement along the boundary.  
This causes robots along the boundary to move more slowly than robots in free-space.

Let the control input be a vector force $\vec{F}$ with magnitude $F$ and orientation $\theta$ with respect to a line perpendicular to and into the nearest boundary. $N$ is the normal or perpendicular force between the robot and the boundary. The force of friction $F_f$ is nonzero if the robot is in contact with the boundary and  $\sin(\theta) < 0$. The resulting net force on the robot, $F_{\text{\emph{forward}}}$, is aligned with the wall and given by
\begin{align}
F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
\text{and } N &= F \cos(\theta) \nonumber
\end{align}
 Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. 
Though each receives the same inputs,  they experience different net forces.
  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
This means that if one robot is touching the wall and another robot is free, the touching robot will not move when the control input is parallel or into the wall. 
There are many alternate models of friction that also break control symmetry. Fig.~\ref{fig:friction}c shows fluid flow along a boundary.  Fluid in the free-flow region moves uniformly, but flow decreases to zero in the boundary layer \citep{fluidMechanics}.  
\begin{align}
%u(y) = u_0 \left(1- \frac{(y-h)^2}{h^2}\right) = u_0 \frac{y}{h} \left(2- \frac{y}{h}\right) \label{eq:boundarylayerflow} THiS EQUATION IS TERRIBLE! PLOT IT.
F_{forward}(y) &= F - F_f\begin{cases}  \frac{h-y}{h}   , &  y<h \label{eq:boundarylayerflow} \\
0, & \text{else} \end{cases}
\end{align}

The next section shows how a system in a rectangularly bounded workspace with friction model \eqref{eq:frictionmodel} can arbitrarily position two robots. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{(a,b) Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot. (c) velocity of a fluid reduces to zero at the boundary.
\label{fig:friction}
}\vspace{-1em}
\end{center}
\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.64\columnwidth}
{\begin{overpic}[width =\figwid]{RegionMove1.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove2.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove3.pdf}
\end{overpic}
}\\

\caption{\label{fig:regionMove}{Two rectangles representing the reachable regions for the current start and goal positions. The red square represents the starting $\Delta x$ and $\Delta y$ and the green circle represents the goal $\Delta x$ and $\Delta y$. The green rectangle illustrates one move reachable $\Delta x$ and $\Delta y$ by horizontal walls and the blue rectangle illustrates the vertical walls reachable region.
}
\vspace{-1em}
}
\end{figure*}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of Two Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.32\columnwidth}
{\begin{overpic}[width =\figwid]{story3Moves1.pdf}\put(65,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves2.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves3.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves4.pdf}\put(50,80){Move 3}
\end{overpic}
%\begin{overpic}[width =\figwid]{s5}\put(50,80){Move 4}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S6.pdf}\put(50,80){Move 5}
%\end{overpic}
}\\
{\begin{overpic}[width =\figwid]{story5move0.pdf}\put(10,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move1.pdf}\put(10,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move2.pdf}\put(10,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move3.pdf}\put(10,80){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move4.pdf}\put(10,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move5.pdf}\put(10,80){Move 5}
\end{overpic}
}\\
{\begin{overpic}[width =\figwid]{story7move0.pdf}\put(65,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move1.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move2.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move3.pdf}\put(50,80){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move4.pdf}\put(50,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move5.pdf}\put(50,80){Move 5}
\end{overpic}
}\\

@@

\subsection{Position Control of $n$ Robots Using Wall Friction}\label{sec:PostionControlnRobots}
Alg. \ref{alg:PosControl2Robots}  can be extended to control the position of $n$ robots using wall friction under several constraints. The solution described here is an iterative procedure with $n$ loops. The $k$th loop moves the $k$th robot from a \emph{staging zone} to the desired position in a \emph{build zone}. All robots move according to the global input, but due to wall friction, at the end the $k$th loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. See Fig.~\ref{fig:construction2d} for a schematic of the build and staging zones.
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobotsComp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:simulationNrobot}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=.3\columnwidth]{driftmove.pdf}
	\includegraphics[width=.3\columnwidth]{driftmove2.pdf}
	\includegraphics[width=.3\columnwidth]{driftmove3.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:driftmove}
A  $\operatorname{DriftMove}(\alpha, \beta, \epsilon)$ to the right repeats a triangular movement sequence $\{ (\beta/2,-\epsilon),(\beta/2,\epsilon),(-\alpha,0)\}$. Robot $A$ touching a top wall moves right $\beta$ units, while robots not touching the top move right $\beta-\alpha$.}
\vspace{-1em}
\end{figure}

>>>>

\emph{Using Boundaries: Friction and Boundary Layers}\label{subsec:WallFriction}
Global inputs move a swarm uniformly.  
Shape control requires breaking this uniform symmetry.  
A swarm inside an axis-aligned rectangular workspace can reduce variance normal to a wall by simply pushing the swarm into the boundary. 
%If the swarm can flow around each other, pushing the swarm into a boundary produces the limited set of configurations presented in Sec.~\ref{subsec:FluidInTank}.
%Controlling covariance by pushing the swarm into a boundary requires changes to the boundary.  
%An obstacle in the lower-right corner is enough to generate positive covariance, but generating both positive and negative covariance requires additional obstacles.  
%Requiring a special obstacle configuration also makes shape control dependent on the local environment. 
%Instead of pushing our robots directly into a wall, 
The following sections examine using boundaries that stop the particles if they are pushed into the wall.
 These forces are  sufficient to break the symmetry caused by uniform inputs.  
%Robots touching a wall have a friction force that opposes movement along the boundary.  
%This causes robots along the boundary to move more slowly than robots in free-space.

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
All the robots get shared control input. Here in the left picture the wall has infinite friction. Therefore, when the first robot is touching the wall, the second robot can move to anywhere in the shaded area. We introduce a dynamic algorithm to find the shortest path the robots can move to get to their goal positions. Consider the reflection of the goal position to the wall that is aimed to be touched by one of the robots. In the right picture, it is shown that the shortest path with three moves is the straight line between the starting position of the robot and the reflection of the goal.
} \vspace{-1em}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{Reflection.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
All the robots get shared control input. Here in the left picture the wall has infinite friction. Therefore, when the first robot is touching the wall, the second robot can move to anywhere in the shaded area. We introduce a dynamic algorithm to find the shortest path the robots can move to get to their goal positions. Consider the reflection of the goal position to the wall that is aimed to be touched by one of the robots. In the right picture, it is shown that the shortest path with three moves is the straight line between the starting position of the robot and the reflection of the goal.
} \vspace{-1em}
\end{figure}

%Let the control input be a vector force $\vec{F}$ with magnitude $F$ and orientation $\theta$ with respect to a line perpendicular to and into the nearest boundary. $N$ is the normal or perpendicular force between the robot and the boundary. The force of friction $F_f$ is nonzero if the robot is in contact with the boundary and  $\sin(\theta) < 0$. The resulting net force on the robot, $F_{\text{\emph{forward}}}$, is aligned with the wall and given by
%\begin{align}
%F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
%\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
%F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
%\text{and } N &= F \cos(\theta) \nonumber
%\end{align}
% Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. 
%Though each receives the same inputs,  they experience different net forces.
%  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
%This means that if one robot is touching the wall and another robot is free, the touching robot will not move when the control input is parallel or into the wall. 
%There are many alternate models of friction that also break control symmetry. Fig.~\ref{fig:friction}c shows fluid flow along a boundary.  Fluid in the free-flow region moves uniformly, but flow decreases to zero in the boundary layer \citep{fluidMechanics}.  
%\begin{align}
%%u(y) = u_0 \left(1- \frac{(y-h)^2}{h^2}\right) = u_0 \frac{y}{h} \left(2- \frac{y}{h}\right) \label{eq:boundarylayerflow} THiS EQUATION IS TERRIBLE! PLOT IT.
%F_{forward}(y) &= F - F_f\begin{cases}  \frac{h-y}{h}   , &  y<h \label{eq:boundarylayerflow} \\
%0, & \text{else} \end{cases}
%\end{align}
%
%The next section shows how a system in a rectangularly bounded workspace with friction model \eqref{eq:frictionmodel} can arbitrarily position two robots. 
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.8\columnwidth]{friction.pdf} 
%\vspace{-1em}
%\caption{(a,b) Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot. (c) velocity of a fluid reduces to zero at the boundary.
%\label{fig:friction}
%}\vspace{-1em}
%\end{center}
%\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.67\columnwidth}
{\begin{overpic}[width =\figwid]{RegionMove1.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove2.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove3.pdf}
\end{overpic}
}\\

\caption{\label{fig:regionMove}{Workspace and $\Delta$ configuration space for three sets of robot configurations with the same final goal. The red square represents the starting $\Delta x$ and $\Delta y$ and the green circle represents the goal $\Delta x$ and $\Delta y$. The green rectangle illustrates one move reachable $\Delta x$ and $\Delta y$ by horizontal walls and the blue rectangle illustrates the vertical walls reachable region.
}
\vspace{-1em}
}
\end{figure*}

%\section{Algorithms}\label{sec:algorithms}
\section{Position Control of Two Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{story3Moves1.pdf}\put(10,10){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves2.pdf}\put(10,10){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves3.pdf}\put(10,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves4.pdf}\put(10,10){Move 3}
\end{overpic}
%\begin{overpic}[width =\figwid]{s5}\put(50,80){Move 4}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S6.pdf}\put(50,80){Move 5}
%\end{overpic}
}\\

%\vspace{1em}
{
\begin{overpic}[width =\figwid]{story5move1.pdf}\put(10,10){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move2.pdf}\put(10,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move3.pdf}\put(10,10){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move4.pdf}\put(10,10){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move5.pdf}\put(10,10){Move 5}
\end{overpic}
}\\

%\vspace{1em}
{
\begin{overpic}[width =\figwid]{story7move1.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move2.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move5.pdf}\put(50,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move6.pdf}\put(50,80){Move 6}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move7.pdf}\put(50,80){Move 7}
\end{overpic}
}\\

@@

\section{Position Control of $n$ Robots Using Wall Friction}\label{sec:PostionControlnRobots}
Alg. \ref{alg:PosControl2Robots}  can be extended to control the position of $n$ robots using wall friction under several constraints. The solution described here is an iterative procedure with $n$ loops. The $k$th loop moves the $k$th robot from a \emph{staging zone} to the desired position in a \emph{build zone}. All robots move according to the global input, but due to wall friction, at the end the $k$th loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. See Fig.~\ref{fig:construction2d} for a schematic of the build and staging zones.
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobots.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:simulationNrobot}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=.47\columnwidth]{driftmove0.pdf}
	\includegraphics[width=.47\columnwidth]{driftmove1.pdf}
	\includegraphics[width=.47\columnwidth]{driftmove2.pdf}
	\includegraphics[width=.47\columnwidth]{driftmove3.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:driftmove}
A  $\operatorname{DriftMove}(\alpha, \beta, \epsilon)$ to the right repeats a triangular movement sequence $\{ (\beta/2,-\epsilon),(\beta/2,\epsilon),(-\alpha,0)\}$. Robot $A$ touching a top wall moves right $\beta$ units, while robots not touching the top move right $\beta-\alpha$.}
\vspace{-1em}
\end{figure}
